% Cover letter using letter.cls
\documentclass{letter} % Uses 10pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8.5in    % text height can be bigger for a longer letter
\oddsidemargin=0pt   % leftmargin is 1 inch
\textwidth=6.5in     % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Eric Timmerman}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
 
\begin{letter}{OSL Hiring Staff \\
OSU Open Source Lab \\
Kerr Admin B211\\
Corvallis, OR 97331}

\begin{center}
{\large\bf Eric Timmerman} 
\end{center}
\medskip\hrule height 1pt
\begin{center}
{935 NW Hobart Ave. Apt 22 \\   Corvallis, OR 97330 \\ (503) 899-5085 or eet1992@yahoo.com \\  https://github.com/clantant} 
\end{center} \vfill % forces letterhead to top of page
 
 
\opening{Dear OSL Hiring Staff:} 
 
\noindent I am applying for the Student Systems Engineer position that I learned about from OSL's employment page at http://osuosl.org/about/employment.
This letter serves to clear up a few pieces of the resume and capture information that is not on it currently.
 
\noindent As a Electrical and Computer Engineering and Computer Science double major I see systems engineering as a very good fusion of computer software and hardware. I have enjoyed my time working with consumer systems, having designed my current desktop with upgrades over time. I have also broken and fixed my Windows system multiple times and worked with Linux on the side with my netbook currently running Windows 7 and Backtrack 5. In regards to my analytic skills it comes from my experience working in boy scouts having to plan events and lead groups. It also comes from how my brain naturally breaks problems into their pieces making it easier to solve them. The server experience that I have is software based not hardware, it comes from CS 275 working with the databases on the onid system. Finally my problem solving skills are helped by analyzing the problem before choosing a solution. I have found importance in keeping in mind all the variables to prevent future problems from coming up. I am currently working for La Sells Stewart Center on campus but I am willing to work solely for OSL and I will be in Corvallis over the summer. I will also be at OSU for at least 2 more years so I will be available that whole time.

 
\noindent I hope that you will consider me for interview and I would just have to work around my class schedule. My best days are Tuesday and Thursday with after 1:30 on Tuesday I am completely free and for Thursday I have a block between 1:30 and 4 PM. My number is 503-899-5085 and can be called any time of the day, if I cannot answer because of class I will reply as soon as possible. Thank you for considering my resume and cover letter and I hope you have a great day.
 
\closing{Sincerely yours,} 
 

 
					% Enclosures

\end{letter}
 

\end{document}
