% LaTeX resume using res.cls
\documentclass[mm]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion
\usepackage{multicol}
\usepackage{geometry}
\geometry{
top = .5in,
bottom = .5in,
left = .5in,
right = 1.75in,
}


\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Eric Timmerman}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width 8in height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{12410 SW Center St, Apt 95}
 \moveleft.5\hoffset\centerline{Beaverton, OR 97005}
 \moveleft.5\hoffset\centerline{phone: (503) 899-5085  email: eet1992@gmail.com}
 \moveleft.5\hoffset\centerline{https://github.com/clantant}


\begin{resume}
 
\section{CAREER OVERVIEW} Systems engineer with a focus on Linux and packaging with the Redhat packaging manager (RPM)
\section{EDUCATION}	{\sl Bachelor of Science,} Computer Science \\
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font
               Oregon State University, Corvallis, OR, expected December 2015: 3.15 GPA \\
                Coursework in software engineering, database design, operating systems, data structures
 
 
\section{QUALIFICATIONS} 
\begin{multicols}{2}
\begin{itemize}
	\item Strong analytical skills
	\item Excellent problem solving skills
	\item Programming and design skills
	\item Leadership 
\end{itemize}
\end{multicols}
 
\section{WORK \\ EXPERIENCE}  
	\textbf{Systems Engineer} \\
	July 2015 to Present \\
	\textbf{CDK Global} - Portland, Oregon \\
\begin{itemize}
	\item Debugging large software stacks to find optimal solutions.
	\item Working with legacy code to update to a new kernel.
	\item Build and port patches to common Linux software packages.
\end{itemize}
	\textbf{Release Engineering Intern} \\
	June 2014 to September 2014 \\
	\textbf{Puppet Labs} - Portland, Oregon \\
\begin{itemize} \parskip0pt \parsep0pt \itemsep-8pt
	\item Worked on software packaging and build automation using Ruby and Rake. \\
	\item Using Linux repackaged multiple packages for AIX, Mac OS X, Solaris, Debian, and Redhat. \\
	\item Created a solution for Ruby Gem signing using GPG detached signing. \\
	\item Integrated with the full time team and worked in the same capacity as a full release engineer. \\
\end{itemize}

\section{EXTRA \\ NOTES}     
	Implementation
		\begin{itemize}
			\item Puppet Fundamentals trained
			\item Multiple C projects using POSIX mutexes, sockets, and threads
			\item Python programs with system communications
		\end{itemize}    
            Leadership
		\begin{itemize}
			\item Eagle Scout Award (Boy Scouting)
			\item Vigil honor (Honor Society of Scouting)
		\end{itemize}
	Design
		\begin{itemize}
			\item Waterfall process for a mobile app to find carpooling possibilities (class, did not implement)
			\item Agile process for a website for people to give away their free stuff (class, partially implemented)
			\item Algorithm principles, implemented travelling salesman problem with genetic algorithm (class)
      \item Auction software from the ground up using python, flask, and sqlite. (side project)
		\end{itemize}
	Embedded Software
		\begin{itemize}
			\item Built several assembly projects with an Atmega 128 chip
      \item Working on a Feline Health Tracking system in a cross-discipline (ECE/CS) senior design project.
 		\end{itemize}

\end{resume}
\end{document}




