%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Systems Engineer} % Job title
    {CDK Global} % Organization
    {Portland, Oregon} % Location
    {July 2015 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Debugged large software stacks on a system level}
        \item {Modified legacy software to work on 64 bit systems}
        \item {Worked with CentOS products and packages to support application level development}
        \item {Using RPM and make revamped an old recursive make to allow for modular building and continous integration}
        \item {Worked on major operating system project as a pivotal resource that pushed it forward}
        \item {Changed between tcl, php, ksh, bash, C, and python on the fly to effectively find the source of many problems}
        \item {Debugged old postgresql and pick commands for newer standards}
        \item {Triaged and corrected a terminal based menu system}
        \item {Using ansible managed virtual machines in an upgrading process}
        \item {Used Git, Confluence, Jira, and Agile Methodology}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Release Engineering Intern} % Job title
    {Puppet} % Organization
    {Portland, Oregon} % Location
    {June 2014 - September 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on software packaging and build automation using Ruby and Rake}
        \item {Using Linux repackaged multiple packages for AIX, Mac OS X, Solaris, Debian, and Redhat}
        \item {Created a solution for Ruby Gem signing using GPG detached signing}
        \item {Integrated with the full time team and worked in the same capacity as a full release engineer}
        \item {Used Git, Confluence, Jira, and Agile Methodology}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Researcher for <Detecting video’s torrents using image similarity algorithms>} % Job title
    {Undergraduate Research, Computer Vision Lab(Prof. Bohyung Han)} % Organization
    {Pohang, S.Korea} % Location
    {Sep. 2012 - Feb. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched means of retrieving a corresponding video based on image contents using image similarity algorithm.}
        \item {Implemented prototype that users can obtain torrent magnet links of corresponding video relevant to an image on web site.}
      \end{cvitems} 
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Trainee} % Job title
    {Software Maestro (funded by Korea Ministry of Knowledge and Economy)} % Organization
    {Seoul, S.Korea} % Location
    {Jul. 2012 - Jun. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Performed research memory management strategies of OS and implemented in Python an interactive simulator for Linux kernel memory management.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {ShitOne Corp. (Start-up company)} % Organization
    {Seoul, S.Korea} % Location
    {Dec. 2011 - Feb. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a proxy drive smartphone application which connects proxy driver and customer. Implemented overall Android application logic and wrote API server for community service, along with lead engineer who designed bidding protocol on raw socket and implemented API server for bidding.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelance Penetration Tester} % Job title
    {SAMSUNG Electronics} % Organization
    {S.Korea} % Location
    {Sep. 2013, Mar. 2011 - Oct. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted penetration testing on SAMSUNG KNOX, which is solution for enterprise mobile security.}
        \item {Conducted penetration testing on SAMSUNG Smart TV.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
